%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Front Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% apply front page header and footer settings here
\thispagestyle{frontpage}

% fields for name and matriculation number
\iftoggle{isGerman}{
	Name: \hspace{7cm} Matrikelnummer:
}{
	Name: \hspace{7cm} Matriculation Number:
}\vspace{-10pt}
\\
\rule{\textwidth}{0.5pt}


\begin{center}
	% title and ID
	{\Large\bf\sc
		\iftoggle{isGerman}
		{
			Klausur
		}
		{
			Exam
		}
	\examID\\ in \\
	\examTitleLong \\}\vspace{1.0cm}
	
	% date
	\examDate

\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Exam Regulations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{put your own regulations here!}

\underline{Permitted aids:}

Slide-rule or {\bf {non}}programmable calculator, \textbf{maximally 1 handwritten DIN A4 sheet}, dictionaries ({\bf non-electronic}), writing and drawing material.
    
Using non-permitted aids like \textbf{scratch paper}, script, lecture notes, books, copies, programmable calculators or laptops is a deceit and leads to the non-admission of the exam.\\
  
\underline{Please note:}
\begin{enumerate}
	\item Write your \textbf{name} and \textbf{matriculation number} on every sheet.
	\item The calculations and solutions to the problems must be written on the related pages. If the space is not sufficient, further sheets are provided. Solutions on those sheets will be considered 
	      only if there exists a reference to the problem and the solution on the extra sheet is marked correspondingly.
	\item Don't write with a pencil. Don't use red or green color.
	\item {\bf Generally every solution must be proved by calculation or explanation.}
\end{enumerate}
    
\underline{Statement:}

With accepting the exam I declare to be able to participate in the exam \examTitleLong~according to my health status.
